%% Modern CV Template Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{red}
\usepackage[utf8]{inputenc}               
\usepackage[scale=0.8]{geometry}

\usepackage[backend=biber,style=authoryear,sorting=ydnt,dashed=false,maxbibnames=99]{biblatex}


\renewbibmacro*{date}{}
\renewbibmacro*{date+extrayear}{}
\newcommand*{\bibyear}{}

\defbibenvironment{bibliography}
  {\list
     {\iffieldequals{year}{\bibyear}
        {}
        {\textbf{\printfield{year}}%
         \savefield{year}{\bibyear}}}
     {\setlength{\topsep}{0pt}% layout parameters based on moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \setlength{\itemsep}{\bibitemsep}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}
 

\addbibresource{cook.bib}


\DeclareFieldFormat
  [article,presentation]
  {title}{\textbf{#1}}

\DeclareFieldFormat{url}{\newline\mkbibacro{URL}\addcolon\space\url{#1}}
 \DeclareFieldFormat{doi}{%
   \mkbibacro{DOI}\addcolon\space
   \ifhyperref
     {\href{http://dx.doi.org/#1}{\nolinkurl{#1}}}
     {\nolinkurl{#1}}}

 \DeclareFieldFormat{pmid}{%
   \mkbibacro{PMID}\addcolon\space
   \ifhyperref
     {\href{http://www.ncbi.nlm.nih.gov/pubmed/#1}{\nolinkurl{#1}}}
     {\nolinkurl{#1}}}

\newbibmacro*{pubmed}{%
\printfield[pmidformat]{pmid}%
}

\DeclareBibliographyDriver{article}{%
  \printtext[bold]{\printfield{title}}%
  \\
  \footnotesize{\printnames{author}}
  \\
  \usebibmacro{journal+issuetitle}\printfield{pmid}\hspace{8pt}\printfield{doi}
  \finentry\\}

\DeclareFieldFormat
  [presentation]
  {title}{\textbf{#1}}

\DeclareBibliographyDriver{presentation}{%
  \printtext[bold]{\printfield{title}}%
  \\
  \printfield{publisher}%
  \printfield{type} --  \printfield{location}%
  \finentry\\}


% personal data
\name{Daniel E.}{Cook}
\address{2850 N. Sheridan Rd. Apt 409}{Chicago, IL. 60657}
\phone[fixed]{773-382-0440}
\email{danielecook@gmail.com}
\homepage{danielecook.com}                   

\begin{document}
\makecvtitle

\section{Education}
\cventry{Expected 2017}{Ph.D. Graduate Student --}{Northwestern University}{Evanston, IL}{Interdisciplinary Program in Biological Sciences (IBiS)}{}

\cventry{May 2010}{B.S. Biology with Honors}{University of Iowa}{Iowa City, IA}{}{}



\section{Experience}


%
% Andersen Lab
%


\cventry{2014--Present}{Graduate Student}{Andersen Lab, Northwestern University}{Evanston, IL}{\textit{}}{%
\begin{itemize}%
\item Developed bioinformatic pipelines population resequencing analysis of \textit{C. elegans}.
\item Created and have maintained laboratory website.
\end{itemize}
}

%
% Ober Lab
%


\cventry{2012-2013}{Research Assistant}{Ober Lab, University of Chicago}{Chicago, IL}{}{%
\begin{itemize}%
\item Assisted with development of databases for phenotypic and genotypic data.
\item Helped disclose carrier status to individuals.
\end{itemize}
}

%
% Murray Lab
%

\cventry{2009-2012}{Research Assistant}{Murray Lab, University of Iowa}{Iowa City, IL}{}{%
\begin{itemize}%
\item Wrote and published statistical, data-management, and graphing programs.
\item Conducted geographic analysis of Iowa newborn screen data.
\item Collected Human Placental tissue for genetic, epigenetic, and expression studies.
\end{itemize}
}





\section{Skills}
\cvdoubleitem{Programming}{Python, Bash, R, Stata, Travis C.I.}{Database}{MySQL, Postgres, SQLite, BigQuery}
\cvdoubleitem{Web}{HTML, Javascript, CSS, Django, Flask,\\ Mediawiki, Wordpress}{Genetic Analysis}{BWA, Samtools, Bcftools, Plink, Galaxy}
\cvdoubleitem{Cloud/Cluster}{AWS, Google Cloud, SLURM}{General}{\LaTeX, sketch}
\cvdoubleitem{Package Development}{R, Python}

\section{Professional Activities}
\begin{itemize}%
\item \textbf{2015} - NSF-GRFP data workshop
\item \textbf{2015} - Teaching Assistant, Genetic Analysis
\item \textbf{2014} - Contributed to development of computational bootcamp for incoming graduate students within the IBiS program.
\end{itemize}

\section{Honors and Awards}
\begin{itemize}%
\item \textbf{2015} - IBiS Travel Award (\$975)
\item \textbf{2014} - National Science Foundation Graduate Research Fellowship 
\item \textbf{2006} - University of Iowa National Scholars Award
\end{itemize}


\newpage
\section{Publications}

\nocite{*}


\printbibliography[type=article,heading=none]
\newpage
\section{Presentations}
\begin{refsection}
\nocite{*}
\printbibliography[type=presentation,heading=none]
\end{refsection}

\end{document}
